---
title: "Final Project"
author: "Holly Christensen"
date: "October 19, 2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(readxl)
```

```{r, echo=FALSE}
rollingsales_manhattan <- read_excel("rollingsales_manhattan.xls", skip = 4) 
manhattan <- rollingsales_manhattan %>% 
  filter(`BUILDING CLASS CATEGORY` == c("01 ONE FAMILY DWELLINGS", "02 TWO FAMILY DWELLINGS", "03 THREE FAMILY DWELLINGS", "07 RENTALS - WALKUP APARTMENTS", "08 RENTALS - ELEVATOR APARTMENTS", "09 COOPS - WALKUP APARTMENTS", "10 COOPS - ELEVATOR APARTMENTS"), `SALE PRICE` <= 10000000) %>% 
  group_by(`BUILDING CLASS CATEGORY`, `NEIGHBORHOOD`)

```

```{r, echo=FALSE}
library(shiny)


ui <- fluidPage(titlePanel("Manhattan Housing Data"), h2("by Holly Christensen"), sidebarLayout(
  sidebarPanel(sliderInput("priceInput", "Price", min = 0, max = 10000000,
            value = c(25, 40), pre = "$"), radioButtons("typeInput", "Housing type",
            choices = c("ONE FAMILY", "TWO FAMILY", "THREE FAMILY", "RENTAL WALK-UP", "RENTAL ELEVATOR", "COOP WALK-UP", "COOP ELEVATOR")), selectInput("areaInput", "Neighborhood",
            choices = c("ALPHABET CITY", "CHELSEA", "CHINATOWN", "CIVIC CENTER", "CLINTON", "EAST VILLAGE", "FASHION", "FINANCIAL", "FLATIRON", "GRAMERCY", "GREENWICH VILLAGE-CENTRAL", "GREENWICH VILLAGE-WEST", "HARLEM-CENTRAL", "HARLEM-EAST", "HARLEM-UPPER", "HARLEM-WEST", "INWOOD", "JAVITS CENTER", "KIPS BAY", "LITTLE ITALY", "LOWER EAST SIDE", "MANHATTAN VALLEY", "MIDTOWN CBD", "MIDTOWN EAST", "MIDTOWN WEST", "MORNINGSIDE HEIGHTS", "MURRAY HILL", "ROOSEVELT ISLAND", "SOHO", "SOUTHBRIDGE", "TRIBECA", "UPPER EAST SIDE (59-79)", "UPPER EAST SIDE (79-96)", "UPPER EAST SIDE (96-110)", "UPPER WEST SIDE (59-79)", "UPPER WEST SIDE (79-96)", "UPPER WEST SIDE (96-116)", "WASHINGTON HEIGHTS LOWER", "WASHINGTON HEIGHTS UPPER"))),
      mainPanel(
      plotOutput("coolplot"),
      br(), br(),
      tableOutput("results")
    )
  )
)
server <- function(input, output) {
  output$coolplot <- renderPlot({
      
      ggplot(data = manhattan, aes(x = `BUILDING CLASS CATEGORY`, y = `SALE PRICE`, color = `BUILDING CLASS CATEGORY`)) +
        geom_boxplot() +
        labs(x = "Building Class",
             y = "Price",
             title = "Real Estate Pricing by Building Class")
      
   })
}
shinyApp(ui = ui, server = server)
```
```{r}

```


## Project Description

The data I have chose to use is the New York City housing data for Manhattan specifically. Analyzing this data will give me at large, a story of New York, but also give me interesting insight as to what areas of the city are trendy now and where buyers can get a deal. I am particularly interested in how housing prices vary across different neighborhoods within Manhattan This is timely research because the data was updated in September 2018.

## Raw Data


I found the data from this URL: https://www1.nyc.gov/site/finance/taxes/property-rolling-sales-data.page
I will focus my attention on the latest Oct. 2017 - Sept. 2018 data for Manhattan. 

